Simulating an Isolated Dwarf Galaxy with Energetic Feedback and Chemical Yields from Individual Stars

### 2018-07-12 main.tex
final updates for now

\begin{figure*}
\includegraphics[width=0.98\linewidth]{log_NO_panel}
            \caption{\textbf{NEED TO UPDATE:} Three slices in the mid-plane of our dwarf galaxy at an arbitrary time of 350~Myr after the start of star formation showing the variation in gas phase metal abundances. The left slice gives the ratio of the abundance between N and O, while the number density and temperature are shown on the right. }
\label{fig:metal_slices}
\end{figure*}

%The CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams. Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases. Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K), diffuse region in the top left corner. 
As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures. As expected, O is overabundant throughout the ISM, most strongly in the region of recent SN enrichment (top left, dark purple region in log(N/O) / dark red in temperature). However, the relative abundance of N increases significantly in the warmer phases, reaching equipartition (white color in log(N/O)) in many patches throughout the ISM. There are three regions in particular that are overabundant in N (green color).

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM. This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we plan to investigate this point, and potential observational consequences for stellar abundances, in future work.

>>>>

\begin{figure*}
\includegraphics[width=0.98\linewidth]{log_NO_panel}
            \caption{Three slices in the mid-plane of our dwarf galaxy at 300~Myr after the start of star formation showing the variation in gas phase metal abundances. The left slice gives the ratio of the abundance between N and O, normalized to the solar abundance, while the number density and temperature are shown on the right. In each, we mark massive stars with active stellar winds as white points and SNe and AGB-phase enrichment events that occured in the preceeding 5 Myr as black stars and orange diamonds respectively.}
\label{fig:metal_slices}
\end{figure*}

%The CNM consists of cold filaments that connect dense clumps of molecular gas that are readily visible in both diagrams. Distinguishing the WNM and WIM is difficult, but the lower density regions between the cold filaments are dominated by these phases. Gas from a recent SN explosion is clearly visible as the hot (T~$\gtrsim 10^{6}$~K), diffuse region in the top left corner. 
As shown in the left panel, log(N/O) varies significantly over this section of the ISM with notable differences across the various phases and ISM structures. The hottest gas, dominated by recent supernova explosions is overabundant in oxygen, relative to solar (purple). However, the relative abundance of nitrogen increases in the WIM and WNM, being overabundant relative to solar (green).

At our adopted metallicity, nitrogen is predominantly produced in AGB star winds, with very little production in core collapse SNe and winds from more massive stars. Therefore, nitrogen is injected into the ISM with significantly less energy ($v \sim 10$~km~s$^{-1}$) than elements produced in SNe, like oxygen, ($v\sim 10^3$~km~s$^{-1}$). Given the variations in Figure~\ref{fig:metal_slices}, the energetic differences between injection sources can drive abundance variations within the ISM of our dwarf galaxy. The regions most rich in N are sites of recent AGB winds that have yet to mix with the rest of the ISM. This suggests that metal mixing within the ISM (and also metal ejection from the ISM) is species dependent. A more detailed analysis is beyond the scope of this work, but we \textbf{investigate this in detail in Emerick et. al. (in prep.).}
